---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Alex Porter"
date: "8/29/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

It has 1846 rows and 3 columns or variables. These variables are x values, y values, and the name of the dataset.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

(Add code and narrative as needed. Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient. To finish, clean up the narrative by removing these instructions.)

First let's plot the data.

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in the dataset.

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

First we plot the points.

```{r plot-circle}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Then we calculate the correlation.
```{r cor-circle}
dino_data %>%
  summarize(r = cor(x, y))
```

This `r` value is very close to the `r` of dino. They are both about 0.06.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)