---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Alex Porter"
date: "8/29/2019"
output: 
  html_document: 
    fig_height: 5.7142857
    fig_width: 8
    highlight: kate
    theme: flatly
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

It has 1846 rows and 3 columns or variables. These variables are x values, y values, and the name of the dataset.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3


First let's plot the data.

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in the dataset.

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

First we plot the points.

```{r plot-circle}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Then we calculate the correlation.
```{r cor-circle}
dino_data %>%
  summarize(r = cor(x, y))
```

This `r` value is very close to the `r` of dino. They are both about -0.06.

### Exercise 5

Let's plot all the datasets at once, making use of faceting. Each dataset has its own color.
```{r plot-all}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```



Now let's calculate all the `r` values using `group_by`.
```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x,y)) %>%
  print(13)
```

